MSB104_assignment1

### 2023-10-11 MSB104_assignment1.qmd
Final update 11.10.23

```{r}
#| echo: false
#| paged.print: false
# Table with overview of population per region in the countries of Germany, Finland and Romania.
DE_FI_RO_pop |> 
  print(
    n = 5 ,
    width = 100 ,
    )
```

@@

```{r}
#| echo: false
#| paged.print: false
# Table with overview of GPD per region in the countries of Germany, Finland and Romania.
DE_FI_RO_gdp |> 
  print(
    n = 5 ,
    width = 100 ,
    )
```

@@

```{r}
#| echo: false
# Summary for viewing the new dataset. 
summary(merged_data_GDP_PC) 
```

@@

```{r}
#| echo: false
# Created new dataset called GDP_DE_nuts2.
# Filtered sub-regions from Germany by using str_sub to extract a substring from the Sub_regions columns containing the letters DE for Germany.
# Creating new column called id_nuts2 to save the new data for calculating Gini coefficient, for presenting the numbers of regional inequity in Germany at NUTS2 level.
# Next step is to group the numbers of NUTS2 level sorted by the the code of the region in NUTS2 level and year.
# Finally summarise the Gini coefficient numbers of each German region in NUTS2 level by multiplying 1 000 000 with GDP divided by population. 
GDP_DE_nuts2 <- merged_data %>%
  filter(
    str_sub(Sub_regions, start = 1L, end = 2L) == "DE"
  ) |> 
  mutate(
    id_nuts2 = fct(str_sub(Sub_regions, start = 1L, end = 4L))
  ) |> 
  group_by(id_nuts2, Year) %>%
  summarise(
    GDP_per_capita_nuts2_DE = sum(1000000*GDP)/sum(Population)
    ) 
```

@@

```{r}
#| echo: false
# First step is to place the location of the figure caption and name it.
# Secondly, we filter GDP_DE_nuts2 to contain integer starting from 3 and ending with 4. Moreover, in this dataset we only contain vales larger or equal to 0, but less than 50.
# Thirdly, we represent the data in GPD_DE_nuts2 by mapping them in a plot using ggplot, where the x-axis represents year and y-axis represents GPD_per_capita. Furthermore the colour is determined by id_nuts2.
# Fourthly, we use geom_line since this gives a accurate description of our data from Germany.
#| cap-location: bottom
#| fig-cap: "GDP per year."
GDP_DE_nuts2 |>
  filter(
    id_nuts2 %in% DEz1NORTH
  ) |> 
  ggplot(mapping = aes(
    x = Year, 
    y = GDP_per_capita_nuts2_DE, 
    colour = id_nuts2)
    ) +
  geom_line()
```

```{r}
#| echo: false
# Duplicating the same steps for Southern Germany as for the Northern part. 
GDP_DE_nuts2 |>
  filter(
    id_nuts2 %in% DEz2SOUTH
  ) |> 
  ggplot(mapping = aes(
    x = Year, 
    y = GDP_per_capita_nuts2_DE, 
    colour = id_nuts2)
    ) +
  geom_line()
```

@@

In year 2000, the region with highest GDP per capita was Hamburg (DE60), which is located in North Germany, with a GDP of 45,659 €.
Hamburg's high GDP in Germany can be attributed to several key factors.
First, Hamburg is home to a diverse range of industries, including maritime trade, logistics, manufacturing, aviation, and media.
This economic diversification contributes to a robust and stable economy.
Second, the Port of Hamburg is one of Europe's largest and busiest ports.
It serves as a major gateway for international trade, making Hamburg a crucial hub for import and export activities @imfnd.

The region with the lowest GDP per capita was Thüringen (DEG0), which is located in North Germany, with a GDP of 16,139 €.
Thüringen has one of the lowest GDPs in Germany due to several factors.
First, Thüringen has a relatively small and less diversified economy compared to other German states.
It relies heavily on traditional industries such as agriculture and manufacturing, which may not contribute significantly to GDP.
Second, Thüringen has a lower population compared to other regions.
A smaller population can lead to reduced economic output @thuringennd.

@@

In year 2020, the region with highest GDP per capita was still Hamburg (DE60), with a GDP of 64,366 €, and the region with the lowest GDP per capita was still Thüringen (DEG0), with a GDP of 28,874 €.

In Germany in 2020, GDP per capita had an average value (mean) of 39,439 €.
The median value of 38,941 € indicates that the distribution is slightly skewed to the left, with about half of the population having values below the mean.
The higher standard deviation of 8,267 € compared to 2000 quantifies the extent of variation around the mean, suggesting a relatively higher level of variability in economic indicators across the population in 2020.

@@

```{r}
#| echo: false
# Created new dataset called GDP_FI_nuts2.
# Filtered sub-regions from Finland by using str_sub to extract a substring from the Sub_regions columns containing the letters FI for Finland
# Creating new column called id_nuts2 to save the new data for calculating Gini coefficient, for presenting the numbers of regional inequity in Finland at NUTS2 level.
# Next step is to group the numbers of NUTS2 level sorted by the the code of the region in NUTS2 level and year.
# Finally summarise the Gini coefficient numbers of each Finnish region in NUTS2 level by multiplying 1 000 000 with GDP divided by population. 
GDP_FI_nuts2 <- merged_data %>%
  filter(
    str_sub(Sub_regions, start = 1L, end = 2L) == "FI"
  ) |> 
  mutate(
    id_nuts2 = fct(str_sub(Sub_regions, start = 1L, end = 4L))
  ) |> 
  group_by(id_nuts2, Year) %>%
  summarise(
    GDP_per_capita_nuts2_FI = sum(1000000*GDP)/sum(Population)
    ) 
```

```{r}
#| echo: false
# First step is to place the location of the figure caption and name it.
# Secondly, we filter GDP_FI_nuts2 to contain integer starting from 3 and ending with 4. Moreover, in this dataset we only contain vales larger or equal to 0, but less than 50.
# Thirdly, we represent the data in GPD_FI_nuts2 by mapping them in a plot using ggplot, where the x-axis represents year and y-axis represents GPD_per_capita. Furthermore the colour is determined by id_nuts2.
# Fourthly, we use geom_line since this gives a accurate description of our data from Finland
#| cap-location: bottom
#| fig-cap: "GDP per year."
GDP_FI_nuts2 |>
  ggplot(mapping = aes(
    x = Year, 
    y = GDP_per_capita_nuts2_FI, 
    colour = id_nuts2)
    ) +
  geom_line()
```

@@

In year 2000, the region with highest GDP per capita was Helsinki-Uusimaa (FI1B), with a GDP of 36,478 €.
Helsinki-Uusimaa is one of the regions in Finland with the highest GDP per capita for several reasons.
Helsinki, the capital of Finland, is located in the Uusimaa region.
Being the largest city and the national capital, Helsinki serves as the economic, financial, and cultural center of Finland.
It is home to numerous businesses, corporate headquarters, government institutions, and educational and research facilities.
The presence of these institutions contributes significantly to the region's economic activity (**SOURCE**).

The region with the lowest GDP per capita was Pohjois- ja Itä-Suomi (FI1D), with a GDP of 20,605 €.
Pohjois- ja Itä-Suomi is one of the regions in Finland with lower GDP per capita for several reasons.
For instance, its located in Northern and Eastern Finland, which characterized by their vast, sparsely populated areas and harsh climatic conditions.
These factors can limit economic activities in certain sectors, such as agriculture and construction, which may thrive more in milder climates and more densely populated regions (**SOURCE**).

@@

In year 2020, the region with highest GDP per capita was still Helsinki-Uusimaa (FI1B), with a GDP of 55,750 €, and the region with the lowest GDP per capita was still Pohjois- ja Itä-Suomi (FI1D), with a GDP of 36,072 €.

In Finland in 2020, while the average GDP per capita was 41,669 €, there was a noticeable level of income inequality.
Some segments of the population earned significantly more or less than the average, as evidenced by the difference between the mean (41,669 €) and median (38,178€).
The presence of a right-skewed distribution indicates the influence of relatively high-income individuals or regions on the mean value.

Also in the graphs for Finland we see the effects on GDP of the Financial Crisis (2007-2008) and Covid-19.

@@

```{r}
#| echo: false
# Created new dataset called GDP_RO_nuts2.
# Filtered sub-regions from Romania by using str_sub to extract a substring from the Sub_regions columns containing the letters RO for Romania
# Creating new column called id_nuts2 to save the new data for calculating Gini coefficient, for presenting the numbers of regional inequity in Romania at NUTS2 level.
# Next step is to group the numbers of NUTS2 level sorted by the the code of the region in NUTS2 level and year.
# Finally summarise the Gini coefficient numbers of each Romanian region in NUTS2 level by multiplying 1 000 000 with GDP divided by population. 
GDP_RO_nuts2 <- merged_data %>%
  filter(
    str_sub(Sub_regions, start = 1L, end = 2L) == "RO"
  ) |> 
  mutate(
    id_nuts2 = fct(str_sub(Sub_regions, start = 1L, end = 4L))
  ) |> 
  group_by(id_nuts2, Year) %>%
  summarise(
    GDP_per_capita_nuts2_RO = sum(1000000*GDP)/sum(Population)
    ) 
```

```{r}
#| echo: false
# First step is to place the location of the figure caption and name it.
# Secondly, we filter GDP_RO_nuts2 to contain integer starting from 3 and ending with 4. Moreover, in this dataset we only contain vales larger or equal to 0, but less than 50.
# Thirdly, we represent the data in GPD_RO_nuts2 by mapping them in a plot using ggplot, where the x-axis represents year and y-axis represents GPD_per_capita. Furthermore the colour is determined by id_nuts2.
# Fourthly, we use geom_line since this gives a accurate description of our data from Romania
#| cap-location: bottom
#| fig-cap: "GDP per year."
GDP_RO_nuts2 |>
  ggplot(mapping = aes(
    x = Year, 
    y = GDP_per_capita_nuts2_RO, 
    colour = id_nuts2)
    ) +
  geom_line()
```

@@

In year 2000, the region with highest GDP per capita was București-Ilfov (RO32), with a GDP of 3972 €.
București-Ilfov is the region with the highest GDP in Romania for several reasons.
București (Bucharest) is not only the capital city of Romania but also its economic and financial center.
As the capital, it serves as the hub for government institutions, businesses, and financial organizations.
This concentration of administrative and economic activity contributes significantly to the region's GDP (**SOURCE**).

The region with the lowest GDP per capita was Nord-Est (RO21), with a GDP of 1253 €.
Nord-Est is one of the regions in Romania with the lowest GDP for several reasons.
Nord-Est has an economy that is predominantly based on agriculture, which tends to have lower productivity and lower value-added compared to other sectors such as manufacturing, services, or technology.
This agricultural dependency can limit the region's overall economic output (**SOURCE**).

@@

In year 2020, the region with highest GDP per capita was still București-Ilfov (RO32), with a GDP of 26,270 €, and the region with the lowest GDP per capita was still Nord-Est (RO21), with a GDP of 7478 €.

In Romania in 2020, the average GDP per capita was around 11,628 €, however there is still significant variation in income levels across different regions or segments of the population.
The median (9822 €), being lower than the mean (11,628 €), hints at the presence of income inequality or disparities in economic well-being.

Also in the graphs for Romania we see the effects on GDP of the Financial Crisis (2007-2008) and Covid-19.

@@

```{r}
#| echo: false
# Firstly, we add a table caption. 
# Secondly, we remove grouping and then we add a new group containing year, min, max, median, mean, sd and var. 
# Thirdly, we use kable to create a create nicely formatted table.
#| tbl-cap: Descriptive statistics based on Gini coeffisient from NUTS2 level in Germany
Gini_stat_DE_nuts2 |> 
  ungroup() |> 
  select(Year, min, max, median, mean, sd, var) %>%
  kable(digits = 5)
```

```{r}
#| echo: false
# Firstly, we add a table caption at the bottom of the figure. 
# Secondly, we use the data from the dataset merged_temp and the function filter to ensure that the data we receive only represents Germany. 
# Thirdly, we use the function ggplot to presentate the Gini coefficient numbers from Germany in a geom_point. 
#| cap-location: bottom
#| fig-cap: "Gini nuts2 DE."
merged_temp |>
  filter(id_nuts2 %in% DE) |>
  ggplot(mapping = aes(
    x = Year, 
    y = gini_n2, 
    colour = id_nuts2)
    ) +
  geom_point()
```

@@

```{r}
#| echo: false
# Firstly, we add a table caption. 
# Secondly, we remove grouping and then we add a new group containing year, min, max, median, mean, sd and var. 
# Thirdly, we use kable to create a create nicely formatted table.
#| tbl-cap: Descriptive statistics based on Gini coeffisient from NUTS2 level in Finland
Gini_stat_FI_nuts2 |> 
  ungroup() |> 
  select(Year, min, max, median, mean, sd, var) %>%
  kable(digits = 5)
```

```{r}
#| echo: false
# Firstly, we add a table caption at the bottom of the figure. 
# Secondly, we use the data from the dataset merged_temp and the function filter to ensure that the data we receive only represents Finland 
# Thirdly, we use the function ggplot to presentate the Gini coefficient numbers from Finland in a geom_point. 
#| cap-location: bottom
#| fig-cap: "Gini nuts2 FI."
merged_temp |>
  filter(id_nuts2 %in% FI) |>
  ggplot(mapping = aes(
    x = Year, 
    y = gini_n2, 
    colour = id_nuts2)
    ) +
  geom_point()
```

@@

```{r}
#| echo: false
# Firstly, we add a table caption. 
# Secondly, we remove grouping and then we add a new group containing year, min, max, median, mean, sd and var. 
# Thirdly, we use kable to create a create nicely formatted table.
#| tbl-cap: Descriptive statistics based on Gini coeffisient from NUTS2 level in Romania
Gini_stat_RO_nuts2 |> 
  ungroup() |> 
  select(Year, min, max, median, mean, sd, var) %>%
  kable(digits = 5)
```

```{r}
#| echo: false
# Firstly, we add a table caption at the bottom of the figure. 
# Secondly, we use the data from the dataset merged_temp and the function filter to ensure that the data we receive only represents Romania. 
# Thirdly, we use the function ggplot to presentate the Gini coefficient numbers from Romania in a geom_point. 
#| cap-location: bottom
#| fig-cap: "Gini nuts2 RO."
merged_temp |>
  filter(id_nuts2 %in% RO) |>
  ggplot(mapping = aes(
    x = Year, 
    y = gini_n2, 
    colour = id_nuts2)
    ) +
  geom_point()
```

@@

>>>>

```{r}
#| echo: false
#| paged.print: false
#| tbl-cap: Population per sub-region in DE, FI & RO
# Table with overview of population per region in the countries of Germany, Finland and Romania.
DE_FI_RO_pop |> 
  print(
    n = 5 ,
    width = 100 ,
    )
```

@@

```{r}
#| echo: false
#| paged.print: false
#| tbl-cap: GDP per sub-region in DE, FI & RO
# Table with overview of GPD per region in the countries of Germany, Finland and Romania.
DE_FI_RO_gdp |> 
  print(
    n = 5 ,
    width = 100 ,
    )
```

@@

```{r}
#| echo: false
#| tbl-cap: GDP per Capita Calculation
# Summary for viewing the new dataset. 
summary(merged_data_GDP_PC) 
```

@@

```{r}
#| echo: false
#| warning: false
# Created new dataset called GDP_DE_nuts2.
# Filtered sub-regions from Germany by using str_sub to extract a substring from the Sub_regions columns containing the letters DE for Germany.
# Creating new column called id_nuts2 to save the new data for calculating Gini coefficient, for presenting the numbers of regional inequity in Germany at NUTS2 level.
# Next step is to group the numbers of NUTS2 level sorted by the the code of the region in NUTS2 level and year.
# Finally summarise the Gini coefficient numbers of each German region in NUTS2 level by multiplying 1 000 000 with GDP divided by population. 
GDP_DE_nuts2 <- merged_data %>%
  filter(
    str_sub(Sub_regions, start = 1L, end = 2L) == "DE"
  ) |> 
  mutate(
    id_nuts2 = fct(str_sub(Sub_regions, start = 1L, end = 4L))
  ) |> 
  group_by(id_nuts2, Year) %>%
  summarise(
    GDP_per_capita_nuts2_DE = sum(1000000*GDP)/sum(Population)
    ) 
```

@@

```{r}
#| label: fig-regional_gdp_per_year_NG
#| echo: false
#| cap-location: bottom
#| fig-cap: "GDP per capita in year - Northern Germany"
# First step is to place the location of the figure caption and name it.
# Secondly, we filter GDP_DE_nuts2 to contain integer starting from 3 and ending with 4. Moreover, in this dataset we only contain vales larger or equal to 0, but less than 50.
# Thirdly, we represent the data in GPD_DE_nuts2 by mapping them in a plot using ggplot, where the x-axis represents year and y-axis represents GPD_per_capita. Furthermore the colour is determined by id_nuts2.
# Fourthly, we use geom_line since this gives a accurate description of our data from Germany.
GDP_DE_nuts2 |>
  filter(
    id_nuts2 %in% DEz1NORTH
  ) |> 
  ggplot(mapping = aes(
    x = Year, 
    y = GDP_per_capita_nuts2_DE, 
    colour = id_nuts2)
    ) +
  geom_line()
```

```{r}
#| label: fig-regional_gdp_per_year_SG
#| echo: false
#| #| cap-location: bottom
#| fig-cap: "GDP per capita in year - Southern Germany"
# Duplicating the same steps for Southern Germany as for the Northern part. 
GDP_DE_nuts2 |>
  filter(
    id_nuts2 %in% DEz2SOUTH
  ) |> 
  ggplot(mapping = aes(
    x = Year, 
    y = GDP_per_capita_nuts2_DE, 
    colour = id_nuts2)
    ) +
  geom_line()
```

@@

In @fig-regional_gdp_per_year_NG we see that there is a relatively similar trend in GDP growth per year from 2000 to 2020, with the exception of one outlier.
This is the top graph which has a much higher GDP per capita than the other regions.
This region is Hamburg (DE60), which is located in North Germany, which had a GDP per capita of 45,659 € in 2000, and 64,366 € in 2020.
Hamburg is home to a diverse range of industries, including maritime trade, logistics, manufacturing, aviation, and media.
Also, the Port of Hamburg is one of Europe's largest and busiest ports.

The region with the lowest GDP per capita was Thüringen (DEG0), which is located in North Germany, with a GDP of 16,139 € in 2000, and 28,874 € in 2020.
Thüringen has a relatively small and less diversified economy compared to other German states.
It relies heavily on traditional industries such as agriculture and manufacturing, which may not contribute significantly to GDP.
We also note that there is a significant fall in GDP per capita in 2010 for the region Mecklenburg-Vorpommern (DE80).

In @fig-regional_gdp_per_year_SG we see that there is a relatively similar trend in GDP growth per year from 2000 to 2020, with the exception of three outliers.
The first outlier is the top graph (Hamburg) which is significantly higher than the rest.
The two other outliers are the second and third highest graphs, which are also significantly higher, however lower than Hamburg.
These regions are Braunschweig (DE91), where we find Wolfsburg, and Bremen (DE50).
We also note that there is a significant fall in GDP per capita in 2010 for the regions Chemnitz (DED4) and Leipzig (DED5).

@@

In 2020, GDP per capita had an average value (mean) of 39,439 €.
The median value of 38,941 € indicates that the distribution is slightly skewed to the left, with about half of the population having values below the mean.
The higher standard deviation of 8,267 € compared to 2000 quantifies the extent of variation around the mean, suggesting a relatively higher level of variability in economic indicators across the population in 2020.

@@

```{r}
#| echo: false
#| warning: false
# Created new dataset called GDP_FI_nuts2.
# Filtered sub-regions from Finland by using str_sub to extract a substring from the Sub_regions columns containing the letters FI for Finland
# Creating new column called id_nuts2 to save the new data for calculating Gini coefficient, for presenting the numbers of regional inequity in Finland at NUTS2 level.
# Next step is to group the numbers of NUTS2 level sorted by the the code of the region in NUTS2 level and year.
# Finally summarise the Gini coefficient numbers of each Finnish region in NUTS2 level by multiplying 1 000 000 with GDP divided by population. 
GDP_FI_nuts2 <- merged_data %>%
  filter(
    str_sub(Sub_regions, start = 1L, end = 2L) == "FI"
  ) |> 
  mutate(
    id_nuts2 = fct(str_sub(Sub_regions, start = 1L, end = 4L))
  ) |> 
  group_by(id_nuts2, Year) %>%
  summarise(
    GDP_per_capita_nuts2_FI = sum(1000000*GDP)/sum(Population)
    ) 
```

```{r}
#| label: fig-regional_gdp_per_year_FI
#| echo: false
#| #| cap-location: bottom
#| fig-cap: "GDP per capita in year - Finland"
# First step is to place the location of the figure caption and name it.
# Secondly, we filter GDP_FI_nuts2 to contain integer starting from 3 and ending with 4. Moreover, in this dataset we only contain vales larger or equal to 0, but less than 50.
# Thirdly, we represent the data in GPD_FI_nuts2 by mapping them in a plot using ggplot, where the x-axis represents year and y-axis represents GPD_per_capita. Furthermore the colour is determined by id_nuts2.
# Fourthly, we use geom_line since this gives a accurate description of our data from Finland
GDP_FI_nuts2 |>
  ggplot(mapping = aes(
    x = Year, 
    y = GDP_per_capita_nuts2_FI, 
    colour = id_nuts2)
    ) +
  geom_line()
```

@@

In @fig-regional_gdp_per_year_FI we see that there is a relatively similar trend in GDP growth per year from 2000 to 2020, with the exception of one outlier.
This is the top graph which has a much higher GDP per capita than the other regions.
This region is Helsinki-Uusimaa (FI1B) which had a GDP per capita of 36,478 € in 2000, and 55,750 € in 2020.
Helsinki, the capital of Finland, is located in the Uusimaa region.
Being the largest city and the national capital, Helsinki serves as the economic, financial, and cultural center of Finland.

The region with the lowest GDP per capita was Pohjois- ja Itä-Suomi (FI1D), with a GDP of 20,605 € in 2000, and 36,072 € in 2020.
Pohjois- ja Itä-Suomi is located in Northern and Eastern Finland, which characterized by their vast, sparsely populated areas and harsh climatic conditions.
These factors can limit economic activities in certain sectors.

@@

In Finland in 2020, while the average GDP per capita was 41,669 €, there was a noticeable level of income inequality.
Some segments of the population earned significantly more or less than the average, as evidenced by the difference between the mean (41,669 €) and median (38,178€).
The presence of a right-skewed distribution indicates the influence of relatively high-income individuals or regions on the mean value.
Also in the graphs for Finland we see the effects on GDP of the Financial Crisis (2007-2008) and Covid-19.

@@

```{r}
#| echo: false
#| warning: false
# Created new dataset called GDP_RO_nuts2.
# Filtered sub-regions from Romania by using str_sub to extract a substring from the Sub_regions columns containing the letters RO for Romania
# Creating new column called id_nuts2 to save the new data for calculating Gini coefficient, for presenting the numbers of regional inequity in Romania at NUTS2 level.
# Next step is to group the numbers of NUTS2 level sorted by the the code of the region in NUTS2 level and year.
# Finally summarise the Gini coefficient numbers of each Romanian region in NUTS2 level by multiplying 1 000 000 with GDP divided by population. 
GDP_RO_nuts2 <- merged_data %>%
  filter(
    str_sub(Sub_regions, start = 1L, end = 2L) == "RO"
  ) |> 
  mutate(
    id_nuts2 = fct(str_sub(Sub_regions, start = 1L, end = 4L))
  ) |> 
  group_by(id_nuts2, Year) %>%
  summarise(
    GDP_per_capita_nuts2_RO = sum(1000000*GDP)/sum(Population)
    ) 
```

```{r}
#| label: fig-regional_gdp_per_year_RO
#| echo: false
#| #| cap-location: bottom
#| fig-cap: "GDP per capita in year - Romania"
# First step is to place the location of the figure caption and name it.
# Secondly, we filter GDP_RO_nuts2 to contain integer starting from 3 and ending with 4. Moreover, in this dataset we only contain vales larger or equal to 0, but less than 50.
# Thirdly, we represent the data in GPD_RO_nuts2 by mapping them in a plot using ggplot, where the x-axis represents year and y-axis represents GPD_per_capita. Furthermore the colour is determined by id_nuts2.
# Fourthly, we use geom_line since this gives a accurate description of our data from Romania
GDP_RO_nuts2 |>
  ggplot(mapping = aes(
    x = Year, 
    y = GDP_per_capita_nuts2_RO, 
    colour = id_nuts2)
    ) +
  geom_line()
```

@@

In @fig-regional_gdp_per_year_RO we see that there is a relatively similar trend in GDP growth per year from 2000 to 2020, with the exception of one outlier.
This is the top graph which has a much higher GDP per capita than the other regions.
This region is București-Ilfov (RO32), which had a GDP of 3972 €, and 26,270 € in 2020.
București (Bucharest) is not only the capital city of Romania but also its economic and financial center.
As the capital, it serves as the hub for government institutions, businesses, and financial organizations.

The region with the lowest GDP per capita was Nord-Est (RO21), with a GDP of 1253 € in 2000, and 7478 € in 2020.
Nord-Est has an economy that is predominantly based on agriculture, which tends to have lower productivity and lower value-added compared to other sectors such as manufacturing, services, or technology.

@@

In 2020, the average GDP per capita was around 11,628 €, however there is still significant variation in income levels across different regions or segments of the population.
The median (9822 €), being lower than the mean (11,628 €), hints at the presence of income inequality or disparities in economic well-being.
Also in the graphs for Romania we see the effects on GDP of the Financial Crisis (2007-2008) and Covid-19.

@@

```{r}
#| echo: false
#| tbl-cap: Descriptive statistics based on Gini coeffisient from NUTS2 level in Germany
# Firstly, we add a table caption. 
# Secondly, we remove grouping and then we add a new group containing year, min, max, median, mean, sd and var. 
# Thirdly, we use kable to create a create nicely formatted table
Gini_stat_DE_nuts2 |> 
  ungroup() |> 
  select(Year, min, max, median, mean, sd, var) %>%
  kable(digits = 5)
```

```{r}
#| label: fig-regional_gini_per_year_RO
#| echo: false
#| #| cap-location: bottom
#| fig-cap: "GDP per capita in year - Romania"
# Firstly, we add a table caption at the bottom of the figure. 
# Secondly, we use the data from the dataset merged_temp and the function filter to ensure that the data we receive only represents Germany. 
# Thirdly, we use the function ggplot to presentate the Gini coefficient numbers from Germany in a geom_point. 
merged_temp |>
  filter(id_nuts2 %in% DE) |>
  ggplot(mapping = aes(
    x = Year, 
    y = gini_n2, 
    colour = id_nuts2)
    ) +
  geom_point()
```

@@

```{r}
#| echo: false
#| tbl-cap: Descriptive statistics based on Gini coeffisient from NUTS2 level in Finland
# Firstly, we add a table caption. 
# Secondly, we remove grouping and then we add a new group containing year, min, max, median, mean, sd and var. 
# Thirdly, we use kable to create a create nicely formatted table.
Gini_stat_FI_nuts2 |> 
  ungroup() |> 
  select(Year, min, max, median, mean, sd, var) %>%
  kable(digits = 5)
```

```{r}
#| label: fig-regional_gini_nuts2_Finland
#| echo: false
#| cap-location: bottom
#| fig-cap: "Gini coefficient numbers on nuts2 level per year in Finland"
# Firstly, we add a table caption at the bottom of the figure. 
# Secondly, we use the data from the dataset merged_temp and the function filter to ensure that the data we receive only represents Finland 
# Thirdly, we use the function ggplot to presentate the Gini coefficient numbers from Finland in a geom_point. 
merged_temp |>
  filter(id_nuts2 %in% FI) |>
  ggplot(mapping = aes(
    x = Year, 
    y = gini_n2, 
    colour = id_nuts2)
    ) +
  geom_point()
```

@@

```{r}
#| echo: false
#| tbl-cap: Descriptive statistics based on Gini coeffisient from NUTS2 level in Romania
# Firstly, we add a table caption. 
# Secondly, we remove grouping and then we add a new group containing year, min, max, median, mean, sd and var. 
# Thirdly, we use kable to create a create nicely formatted table
Gini_stat_RO_nuts2 |> 
  ungroup() |> 
  select(Year, min, max, median, mean, sd, var) %>%
  kable(digits = 5)
```

```{r}
#| label: fig-regional_gini_nuts2_Romania
#| echo: false
#| cap-location: bottom
#| fig-cap: "Gini coefficient numbers on nuts2 level per year in Romania"
# Firstly, we add a table caption at the bottom of the figure. 
# Secondly, we use the data from the dataset merged_temp and the function filter to ensure that the data we receive only represents Romania. 
# Thirdly, we use the function ggplot to presentate the Gini coefficient numbers from Romania in a geom_point. 
merged_temp |>
  filter(id_nuts2 %in% RO) |>
  ggplot(mapping = aes(
    x = Year, 
    y = gini_n2, 
    colour = id_nuts2)
    ) +
  geom_point()
```

@@

@lessmann_and_seidel2017 state regional inequities can influence economic outcomes.
Moreover, when it comes to the German economy, this is not an exception.
Firstly, some outliers occur in our plot chart.
The region that stands out is the region DE91.
According to @eurostat2022, this region in NUTS2 level is named Braunschweig, which includes NUTS3 level cities like Braunschweig, Saltzgitter and Wolfsburg.

Furthermore, Wolfsburg is a centre for education and research.
Moreover, Wolfsburg is also where the headquarters of Volkswagen AG is based.
The company is one of the biggest companies worldwide.
Wolfsburg is also home to many other national and international businesses like Hexad and Sumitomo.
All these companies contribute to an excellent economic infrastructure.
Taking this into account as well, this might describe why the Gini Coefficient in the region DE91 is above 0.43% and indicates a moderate level of income inequality.

Regarding the region with the lowest Gini coefficient, we find regions in the NUT2 level where the Gini coefficient was zero.
This is also why the minimum value shows a value of zero.
The regions we discovered in this case were Leipzig (DED5), Chemnitz (DED4), Dresden (DED2), Hamburg (DE60) and Berlin (DE30) @eurostat2022. We assume that, in reality, there is no chance for perfect regional equality, and the reason for the Gini coefficient showing a value of zero might indicate that there is missing reported data from these regions.
Moreover, when it comes to standard deviation, it is the year 2016 that stands out.
This indicates that some regions operate with a more significant Gini coefficient than the average of regions in Germany.
According to our calculations, the region that stands out is DE91 (Braunschweig).
Lastly, the mean and median from 2000 until 2010 operate with minor differences.
Still, from 2011 to 2020, we can see that, especially in 2016, there is a significant difference where the mean is 0,02427% greater than the median.
This indicates that the data of Gini coefficients contains a few extreme values.
This value, again, is related to the region DE91 (Braunschweig).

Regarding Finland, the regions with the highest regional inequalities are the regions FI19, which, according to @eurostat2022, is Western Finland, and FI1C, which is Southern Finland.
The most populated cities like Helsinki, Tampere, Turku and Oulu are located in these regions.
Our calculations show that Western Finland (FI19) region had the highest Gini coefficient in 2010.
The cities of Oulu, Tampere and Turku are centres of industrial activities and contribute to investments that impact the Gini coefficient.
Regarding the region with the lowest Gini coefficient, we discovered the same case with Finland as with Germany: Some regions operate with a zero value of the Gini coefficient.
Again, we assume this might have to do with missing reported data.
The region at the NUTS2 level that has a Gini coefficient value at zero is FI20, which, according to @eurostat2022, is Åland.

Moreover, looking at our calculations and the plot chart of Finland, there is a significant drop in regional inequality from 2011 to 2020.
The standard deviation tells us that no regions stand out from others compared to the average of regional inequality.
Furthermore, from 2000 until 2010, the median values are more significant than the mean values, indicating that there are less extreme values of the Gini coefficient and, again, a lower case of regional inequality.

In Romania, four regions have a high Gini coefficient.
According to @eurostat2022, these regions are RO32 ( Bucuresti region), RO31 (Sud-Muntenia) -- surrounding the Bucuresti region, RO22 (Sud-Est), which is the region located along the Black Sea with cities like Constanta and RO42 (Timisoara) where important Romanian industries are located.
Moreover, the region RO22 is a popular tourist destination, and the business targets the tourist market.
The mentioned areas generate income that can influence regional inequality compared to a region like RU12 (Centru).
This region has no administrative power and is defined as a development region.
The region receives funding from the EU and distributes them to cities and other sub-regions.

Furthermore, the region with the highest regional inequality in Romania was Bucuresti in 2020.
The same region experienced the lowest regional inequality in 2006.
Moreover, the median and mean are relatively similar which indicate that the Gini coefficient do not contains any significant extreme value.
Lastly, the low standard deviation indicates that the regional inequalities in Romania are close to the average of regional inequalities the different regions experience.
